[Re] Spike Synchronization and Rate Modulation Differentially Involved in Motor Cortical Function

### 2017-03-29 article/VRostami_JIto_MDenker_SGruen_2016.tex
corrected authors format

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Vahid Rostami,
      Junji Ito,,
      Michael Denker,,
      Sonja Grün,
  },
            pdftitle=
{
[Re] Spike Synchronization and Rate Modulation Differentially Involved in
Motor Cortical Function
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

    \usepackage{authblk}
                        \author[1]{Vahid Rostami}
                    \author[1]{Junji Ito,}
                    \author[1]{Michael Denker,}
                    \author[1,2]{Sonja Grün}
                            \affil[1]{Inst. of Neuroscience \& Medicine (INM-6) and Inst. for Advanced
Simulation (IAS-6), JARA Brain Institute I, Jülich Research Center,
Jülich, Germany}
                    \affil[2]{Theoretical Systems Neurobiology, RWTH Aachen University, Aachen,
Germany}

@@

If the authors of the original paper would not have been accessible, we
would not have been able to reproduce the results. Nevertheless, here
our final validation of the reproduction is based only on a detailed
visual comparison of the original and reproduced figures. In an optimal
scenario, we would be able to exactly validate the results based on a
numerical comparison. To do so, all of the following pieces of
information would have had to be available at hand:

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Vahid Rostami,
      Junji Ito,
      Michael Denker,
      Sonja Grün,
  },
            pdftitle=
{
[Re] Spike Synchronization and Rate Modulation Differentially Involved in
Motor Cortical Function
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

    \usepackage{authblk}
                        \author[1]{Vahid Rostami}
                    \author[1]{Junji Ito}
                    \author[1]{Michael Denker}
                    \author[1,2]{Sonja Grün}
                            \affil[1]{Inst. of Neuroscience \& Medicine (INM-6) and Inst. for Advanced
Simulation (IAS-6), JARA Brain Institute I, Jülich Research Center,
Jülich, Germany}
                    \affil[2]{Theoretical Systems Neurobiology, RWTH Aachen University, Aachen,
Germany}

@@

If the authors of the original paper would not have been accessible, we
would not have been able to reproduce the results. Nevertheless, here
our final validation of the reproduction is based the values extracted
from the vector graphic image (PDF) in the original paper. In an optimal
scenario, we would be able to exactly validate the results based on a
numerical comparison. To do so, all of the following pieces of
information would have had to be available at hand:
